<!--
Declarations for Front Matter
-->

\prelimpages

<!-- 
%
% ----- copyright and title pages
%
-->

\Title{Long-term chronology of subsistence and the role of intensive agriculture in the central part of the Korean peninsula}
\Author{Seungki Kwak}
\Year{2015}
\Program{UW Anthropology}

\Chair{Ben Marwick}{Assistant Professor}{Anthropology Department}
\Signature{Peter Lape}
\Signature{Jim Feathers}
\Signature{Rick Keil}

\copyrightpage

\titlepage  


<!--
%
% ----- abstract
%
-->
\setcounter{page}{-1}
\abstract{%
To come...
}


<!--
%
% ----- contents & etc.
%
-->
\tableofcontents
\listoffigures
\listoftables  
 
<!--
%
% ----- Acknowledgments & dedication
%
-->

\acknowledgments{% \vskip2pc
  % {\narrower\noindent
  The author wishes to express sincere appreciation to
  University of Washington ... more to come.
  % \par}
}


\dedication{\begin{center}to my dear wife, JeeIn\end{center}}


\textpages

<!--
%
% ----- Main body of the thesis: This is where we pull in the indvidual chapter files
%
-->

```{r setup, include=FALSE}
# for hi-res plots
library(knitr)
opts_chunk$set(dev = 'pdf')
# suppress xtable message
library(xtable)
options(xtable.comment = FALSE)
```

```{r, ch1, cache=FALSE, child="chapter1.Rmd"}
```

```{r, ch2, cache=FALSE, child="chapter2.Rmd"}
```

```{r, ch3, cache=FALSE, child="chapter3.Rmd"}
```

```{r, ch4, cache=FALSE, child="chapter4.Rmd"}
```

```{r, ch5, cache=FALSE, child="chapter5.Rmd"}
```

```{r, ch6, cache=FALSE, child="chapter6.Rmd"}
```

```{r, ch7, cache=FALSE, child="chapter7.Rmd"}
```

<!--
%
% ----- end of the main body of the thesis
%
-->

 

\printbibliography

\cleardoublepage\null

\newpage\null\thispagestyle{empty}\newpage

\section{Colophon}
This document was typeset using the \textsf{\XeTeX} typesetting system, and the [uwthesis class](https://github.com/UWIT-IAM/UWThesis) created by [Jim Fox](https://staff.washington.edu/fox/tex/uwthesis.shtml). Other elements of the document formatting source code have been taken from the [Latex, Knitr, and RMarkdown templates for UC Berkeley's graduate thesis](https://github.com/stevenpollack/ucbthesis), and [Dissertate: a LaTeX dissertation template to support the production and typesetting of a PhD dissertation at Harvard, Princeton, and NYU](https://github.com/suchow/Dissertate) 

The body text is set at 11pt with \familydefault. The thesis was written as [R markdown](http://rmarkdown.rstudio.com/)- and \LaTeX -formatted documents, which was converted to PDF using [pandoc](http://pandoc.org/) using [knitr](http://yihui.name/knitr/) with a custom R package.


This PDF was generated on `r Sys.time()` in the following computational environment:

```{r session_info, echo=FALSE}
# which R packages and versions?
sessionInfo()
```

The following depedencies external to R are required: 

```{r non_r_deps, echo=FALSE}
# what other pieces of software?
# devtools::install_github("ropensci/dependencies")
needs <- dependencies::needs()
needs  <- data.frame(`Dependencies external to R` = gsub("\n", "", c(needs$depends$SystemRequirements[
  needs$depends$SystemRequirements != "NULL"], 
  needs$imports$SystemRequirements[
    needs$imports$SystemRequirements != "NULL"])))
kable(needs)
```



```{r git_data, echo=FALSE} 
# what commit is this file at?
library(git2r)
repo <- repository(path = "../..")
last_commit <- commits(repo)[[1]]
```

The current git commit of this file is `r last_commit@sha`, which is on the `r branches(repo)[[1]]@name` branch and was made by `r last_commit@committer@name` on `r when(last_commit)`. The current commit message is "`r last_commit@summary`".

\cleardoublepage\null


