<!--
Declarations for Front Matter
-->

\prelimpages

<!-- 
%
% ----- copyright and title pages
%
-->

\Title{The Suitability of List \LaTeX\ Text Formatter\\
  for Thesis Preparation by Technical and\\
  Non-technical Degree Candidates}
\Author{Seungki Kwak}
\Year{2015}
\Program{UW Anthropology}

\Chair{Name of Chairperson}{Title of Chair}{Department of Chair}
\Signature{First committee member}
\Signature{Next committee member}
\Signature{etc}

\copyrightpage

\titlepage  


<!--
%
% ----- abstract
%
-->
\setcounter{page}{-1}
\abstract{%
This sample dissertation is an aid to students who are attempting
to format their theses with \LaTeX, a sophisticated
text formatter widely used by mathematicians and scientists everywhere.
 
\begin{itemize}
\item It describes the use of a specialized
macro package developed specifically for thesis production
at the University.
The macros customize \LaTeX\ for the correct thesis style,
allowing the student to concentrate on the substance of
his or her text.%
\footnote{See Appendix A to obtain the source to this
 thesis and the class file.}
\item It demonstrates the solutions to a variety of
formatting challenges found in thesis production.
\item It serves as a template for a real dissertation.
\end{itemize}
}


<!--
%
% ----- contents & etc.
%
-->
\tableofcontents
\listoffigures
\listoftables  
 
<!--
%
% ----- Acknowledgments & dedication
%
-->

\acknowledgments{% \vskip2pc
  % {\narrower\noindent
  The author wishes to express sincere appreciation to
  University of Washington, where he has had the opportunity
  to work with the \TeX\ formatting system,
  and to the author of \TeX, Donald Knuth, {\it il miglior fabbro}.
  % \par}
}


\dedication{\begin{center}to my dear wife, JeeIn\end{center}}


\textpages

<!--
%
% ----- Main body of the thesis: This is where we pull in the indvidual chapter files
%
-->

```{r setup, include=FALSE}
# for hi-res plots
knitr::opts_chunk$set(dev = 'pdf')
# suppress xtable message
library(xtable)
options(xtable.comment = FALSE)
```

```{r, ch1, cache=FALSE, child="chapter1.Rmd"}
```

```{r, ch2, cache=FALSE, child="chapter2.Rmd"}
```

```{r, ch3, cache=FALSE, child="chapter3.Rmd"}
```

```{r, ch4, cache=FALSE, child="chapter4.Rmd"}
```

```{r, ch5, cache=FALSE, child="chapter5.Rmd"}
```

<!--
%
% ----- end of the main body of the thesis
%
-->

 

\printbibliography

\cleardoublepage\null

\newpage\null\thispagestyle{empty}\newpage

\section{Colophon}
This document was typeset using the \textsf{\XeTeX} typesetting system originally created by the Jonathan Kew, and the [uwthesis class](https://github.com/UWIT-IAM/UWThesis) created by [Jim Fox](https://staff.washington.edu/fox/tex/uwthesis.shtml). Other elements of the document formatting source code have been taken from the [Latex, Knitr, and RMarkdown templates for UC Berkeley's graduate thesis](https://github.com/stevenpollack/ucbthesis), and [Dissertate: a LaTeX dissertation template to support the production and typesetting of a PhD dissertation at Harvard, Princeton, and NYU](https://github.com/suchow/Dissertate) 

The body text is set at 11pt with \familydefault. The thesis was written as [R markdown](http://rmarkdown.rstudio.com/) and \LaTeX formatted documents, which was converted to PDF using [pandoc](http://pandoc.org/) using [knitr](http://yihui.name/knitr/) with a custom R package.


This PDF was generated on `r Sys.time()` in the following computational environment:

```{r session_info, echo=FALSE}
# which R packages and versions?
sessionInfo()
```

The following depedencies external to R are required: 

```{r non_r_deps, echo=FALSE}
# what other pieces of software?
# devtools::install_github("ropensci/dependencies")
needs <- dependencies::needs()
c(needs$depends$SystemRequirements[
  needs$depends$SystemRequirements != "NULL"], 
  needs$imports$SystemRequirements[
    needs$imports$SystemRequirements != "NULL"])
```

```{r git_data, echo=FALSE} 
# what commit is this file at?
library(git2r)
repo <- repository(path = "../..")
last_commit <- commits(repo)[[1]]
```

The current git commit of this file is `r last_commit@sha`, which is on the `r branches(repo)[[1]]@name` branch and was made by `r last_commit@committer@name` on `r when(last_commit)`. The current commit message is "`r last_commit@summary`".

\cleardoublepage\null


