<!--
Declarations for Front Matter
-->

\prelimpages

<!-- 
%
% ----- copyright and title pages
%
-->

\Title{The Suitability of List \LaTeX\ Text Formatter\\
  for Thesis Preparation by Technical and\\
  Non-technical Degree Candidates}
\Author{Jim Fox}
\Year{1985-2014}
\Program{UW Information Technology}

\Chair{Name of Chairperson}{Title of Chair}{Department of Chair}
\Signature{First committee member}
\Signature{Next committee member}
\Signature{etc}

\copyrightpage

\titlepage  


<!--
The title page generated by LaTeX is now acceptable for handing in.
(This was not always the case).
-->

<!--
%
% ----- abstract
%
-->
\setcounter{page}{-1}
\abstract{%
This sample dissertation is an aid to students who are attempting
to format their theses with \LaTeX, a sophisticated
text formatter widely used by mathematicians and scientists everywhere.
 
\begin{itemize}
\item It describes the use of a specialized
macro package developed specifically for thesis production
at the University.
The macros customize \LaTeX\ for the correct thesis style,
allowing the student to concentrate on the substance of
his or her text.%
\footnote{See Appendix A to obtain the source to this
 thesis and the class file.}
\item It demonstrates the solutions to a variety of
formatting challenges found in thesis production.
\item It serves as a template for a real dissertation.
\end{itemize}
}


<!--
%
% ----- contents & etc.
%
-->
\tableofcontents
\listoffigures
\listoftables  
 


\acknowledgments{% \vskip2pc
  % {\narrower\noindent
  The author wishes to express sincere appreciation to
  University of Washington, where he has had the opportunity
  to work with the \TeX\ formatting system,
  and to the author of \TeX, Donald Knuth, {\it il miglior fabbro}.
  % \par}
}


\dedication{\begin{center}to my dear wife, Joanna\end{center}}


\textpages

<!-- (Optional) \part{First Part} -->

```{r setup, include=FALSE}
# for hi-res plots
opts_chunk$set(dev = 'pdf')
```

```{r, cache=FALSE, child="chapter1.Rmd"}
```

```{r, cache=FALSE, child="chap2.Rmd"}
```


\printbibliography
